Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2013-11-05 writeups/proposal/proposal.tex
foo
Former-commit-id: 63995900765b0c801ce041aaddd6fae53d96882f [formerly a5e8f67726fe5f9f5383f8af8d2701cb5c7d92a3]
Former-commit-id: 95bbbb5a52d52a836c99c1d93201aeac69e4464b

Google+'s tag-recommendation algorithm is not publicized, but it appears to be rather sophisticated.
Looking at the example post in Figure \ref{figGoogle+Hashtags}, \#BusterPosey is suggested without having that specific word in the post.
Also \textcite{GoogleKeynote2013} mentioned that Google uses its sophisticated image recognition software to suggest hashtags for images that are included in the post (e.g., \#EiffelTower),
even when the post does not have any keywords to provide additional context.

>>>>

Google+'s tag-recommendation algorithm is not publicized, but it appears to be rather sophisticated.
Looking at the example post in Figure \ref{figGoogle+Hashtags}, \emph{\#BusterPosey} is suggested without having that specific word in the post.
Also \textcite{GoogleKeynote2013} mentioned that the algorithm uses Google's sophisticated image recognition software to suggest hashtags for images that are included in the post (e.g., \emph{\#EiffelTower}),
even when the post does not have any keywords to provide additional context.
